### 2019-12-21 Statistical Methods/07_hypothesis-testing.rmd
statistical methods, ch7
statistical methods, ch7

Assuming 20% trimming, test the hypothesis $H_0 : \mu = 42, \alpha = 0.05, n = 20$ given the following values for $\bar{X}$ and $s_w$:

@@

@@

@@

@@

Repeat the previous exercise, only test the hypothesis $H_0 : \mu_t \le 42, \alpha = 0.05$

@@

@@

@@

@@

### 7.33
### 7.34
### 7.35
### 7.36
### 7.37

>>>>

Assuming 20% trimming, test the hypothesis $H_0 : \mu = 42, \alpha = 0.05, n = 20$ given the following values for $\bar{X}_t$ and $s_w$:

@@

```{r, echo = T}
xbar <- 44; s <- 9; n <- 20
alpha <- 0.05; h0 <- 42

g <- floor(.2*n)

df <- n - g*2 - 1

crit <- qt(1 - alpha/s, df)

Tval <- .6 * (xbar - h0) / s * sqrt(n)

ifelse(abs(Tval) > crit, "Reject the null", "Cannot reject null")
```

@@

```{r, echo = T}
xbar <- 43; s <- 9;

Tval <- .6 * (xbar - h0) / s * sqrt(n)

ifelse(abs(Tval) > crit, "Reject the null", "Cannot reject null")
```

@@

```{r, echo = T}
xbar <- 43; s <- 3;

Tval <- .6 * (xbar - h0) / s * sqrt(n)

ifelse(abs(Tval) > crit, "Reject the null", "Cannot reject null")
```

@@

Repeat the previous exercise, only test the hypothesis $H_0 : \mu_t \le 42, \alpha = 0.05, n = 16$

@@

```{r, echo = T}
xbar <- 44; s <- 9; n <- 16
alpha <- 0.05

g <- floor(.2*n)

df <- n - g*2 - 1

crit <- qt(1 - alpha, df)

Tval <- .6 * (xbar - h0) / s * sqrt(n)

ifelse(Tval > crit, "Reject the null", "Cannot reject null")
```

@@

```{r, echo = T}
xbar <- 43; s <- 9;

Tval <- .6 * (xbar - h0) / s * sqrt(n)

ifelse(Tval > crit, "Reject the null", "Cannot reject null")
```

@@

```{r, echo = T}
xbar <- 43; s <- 3;

Tval <- .6 * (xbar - h0) / s * sqrt(n)

ifelse(Tval > crit, "Reject the null", "Cannot reject null")
```

@@

### 7.33

A standard measure of aggression in 7-year-old children has been found to have a 20% trimmed mean of 4.8 based on years of experience. A psychologiest wants to know whether the trimmed mean for children with divorced parents is greater than or less than 4.8.

Suppose $\bar{X}_t = 5.1, s_w = 7$ based on $n = 25$

Test $H_0 : \mu_t = 4.8, \alpha = 0.01$

### 7.34

Summarize the relative merits of using a percentile bootstrap method.

### 7.35

For the data in R variable _x_, imagine that you want to compute Z with the goal of testing the hypothesis that $\mu = 6$. Assuming that the R variable _null.value_ contains the hypothesized value and that _sigma_ contains the standard deviation, indicate the R command for computing Z.

test <- (mean(x) - null.value) / sigma * length(x)

### 7.36

R has a built-in data set called _ToothGrowth_. Information about the data can be obtained with the R command ?ToothGrowth. The first column contains measures of tooth growth in guinea pigs and the third column indicates the dose levels of vitaime C that were used in the experiment.

Consider the claim that the typical growth is 8 when the vitamine C level is 0.5 mg. Using R, verify that with Student's T and $\alpha = 0.05$, it would be decided that the population mean is larger than 8.

Verify that no decision would be made based on the Tukey-McLaughlin method with a 20% trimmed mean.

Plot the data and comment why the two methods give different results.

### 7.37

Based on the results for the previous exercise, speculate about whether you would reject using a median or MOM.

Use R to check your speculation.
